Spatial Analysis of Russian Law Firms Naming

### 2024-07-17 law-firms-names/Paper.Rmd
Write paragraphs about the object, scope and goals of the research, #4

>>>>

There are thousands of law firms in Russia [@Moiseeva2016]. Their names are likely to reflect some properties of local legal services market. The area of Russia is comprised of regions (constituent entities of the federation) that provide some sort of a commonly used spatial unit for geographical studies. Besides, economic geographers split the country into 11 economic regions [@Leyzerovich2010]. Each economic regions includes several constituent entities and is characterized by internal integrity, economic links between the companies, specialization and difference from the others. It can be hypothesized that the proximity of regions, as well as internal unity and economic links within the economic regions, leads to the similarity of law firms activity and, correspondingly, to the similarity of their naming. The overall aim of this study is to check whether this is true. To achieve this goal, a few research questions are asked and then answered based on the data on law firms names. These questions, or problems, are specified below.

Question 1 (Q1) is whether the neighboring regions have more similar law firm names that regions that do not share a common border. Question 2 (Q2) is a continuous extension of Q1: whether the geographical proximity of regions has an impact on the similarity of law firm names, i.e. whether the regions that are close to each other have more similar names, and vice versa. Question 3 (Q3) moves up from the level of regions to the level of economic regions: whether names withing the economic region are more similar compared to the names outside the region. Question 4 (Q4) is what naming strategies exist in Russia and how they are spatially organized. Question 5 (Q5) is a follow-up from the previous: are there strategies common or different within each economic region?
